### 2019-01-30 manuscript.tex
Made some changes to the manuscript
changed some plots

@@

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be. As it was possible that participants were aware of their own ability but were not using this information, half of the participants were asked to state after having selected somewhere to stand. This was added as a potential prompt for participants to make use of this information which may have potentially improved performance \citep{chang2014self}. The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial also did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using their knowledge of their ability to accuractely throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the four studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

@@

\begin{figure}[ht!]
	\includegraphics[scale=0.9]{Figures/Experiment_4_prob/Estimated_Accuracy_both}
	\centering
	\captionsetup{justification=centering}
	\caption{These plots show the expected accuracy for each participant given their fixations. The upper limit of the "red" shaded region represents a participants' accuracy should they have exclusively fixated the central box. The upper limit of the darker blue region represents accuracy should the participant have performed optimally in the \textit{Random} condition. The lighter region is the same again, but for the \textit{Biased} condition}
	\label{fig:Session2-prob-accresults}
\end{figure}

>>>>

% \subsection*{Cognitive Biases}
% \addcontentsline{toc}{subsection}{Cognitive Biases}
% Not sure if this is entirely needed to be honest...

@@

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be. As it was possible that participants were aware of their own ability but were not using this information, half of the participants were asked to state after having selected somewhere to stand. This was added as a potential prompt for participants to make use of this information which may have potentially improved performance \citep{chang2014self}. The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial, however, did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using knowledge of their ability to accuractely throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the four studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

@@

%\begin{figure}[ht!]
%\includegraphics[scale=0.9]{Figures/Experiment_4_prob/Estimated_Accuracy_both}
%	\centering
%	\captionsetup{justification=centering}
%	\caption{These plots show the expected accuracy for each participant given their fixations. The upper limit of the "red" shaded region represents a participants' accuracy should they have exclusively fixated the central box. The upper limit of the darker blue region represents accuracy should the participant have performed optimally in the \textit{Random} condition. The lighter region is the same again, but for the \textit{Biased} condition}
%	\label{fig:Session2-prob-accresults}
%\end{figure}

\begin{figure}
	\centering
	\captionsetup{justification=centering}
	\subfloat{\includegraphics[height = 10cm, width = 15cm]{Figures/Experiment_4_prob/exp_vs_opt_bias_lines}}\quad
	\subfloat{\includegraphics[height=10cm,width=15cm]{Figures/Experiment_4_prob/exp_vs_opt_rand_lines}}
	\caption{The different lines represent the predicted accuracy given the particiapnt had employed either the optimal or centre strategy, and their expected accuracy given the fixation locations the participant made in the experiment.}
	\label{fig:Session2-prob-accresults}
\end{figure}
